Enhancement of SDR in Thessaloniki

### 2024-09-05 GHI_enh_03_process.tex
Commit 2024-09-05 12:14

  \usepackage{unicode-math}

@@

@@

\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\urlstyle{same} % disable monospaced font for URLs

@@

\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}

@@

\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}

@@

\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}

@@

\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}

@@

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-08-29}

@@

{
\hypersetup{linkcolor=}
\setcounter{tocdepth}{4}
\tableofcontents
}
\begin{verbatim}
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
   0.00   89.59  180.00  180.00  270.42  360.00 
\end{verbatim}

\begin{verbatim}
    Min.  1st Qu.   Median     Mean  3rd Qu.     Max. 
-72.8133 -27.4712   0.7647   0.4304  28.2448  83.4876 
\end{verbatim}

@@

\hypertarget{time-series-decomposition-tests}{%
\subsection{Time series decomposition tests}\label{time-series-decomposition-tests}}

@@

\begin{verbatim}
Call:
stats::lm(formula = .formula, data = df)

Residuals:
    Min      1Q  Median      3Q     Max 
-317.54 -148.95  -56.71  107.07  717.24

Coefficients:
                  Estimate Std. Error t value Pr(>|t|)   
(Intercept)      1.533e+02  4.805e+01   3.190  0.00155 **
as.numeric(Date) 1.203e-07  3.816e-08   3.153  0.00175 **
---
Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Residual standard error: 197.8 on 354 degrees of freedom
Multiple R-squared:  0.02732,   Adjusted R-squared:  0.02457 
F-statistic: 9.943 on 1 and 354 DF,  p-value: 0.001752
\end{verbatim}

@@

\begin{verbatim}
Call:
lm(formula = ST_E_monthly$wattGLB.N ~ ST_E_monthly$Date)

Residuals:
    Min      1Q  Median      3Q     Max 
-317.54 -148.95  -56.71  107.07  717.24

Coefficients:
                   Estimate Std. Error t value Pr(>|t|)   
(Intercept)       1.533e+02  4.805e+01   3.190  0.00155 **
ST_E_monthly$Date 1.203e-07  3.816e-08   3.153  0.00175 **
---
Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Residual standard error: 197.8 on 354 degrees of freedom
Multiple R-squared:  0.02732,   Adjusted R-squared:  0.02457 
F-statistic: 9.943 on 1 and 354 DF,  p-value: 0.001752
\end{verbatim}

@@

\begin{verbatim}
aa
aatm
aday
adjpoint55
AEin1
All_daily_ratio_lim
alpha
amean
ampl
asza
atype
avar
b
BIO_ELEVA
C4_cs_ref_ratio
C4_GLB_diff_THRES
C4_lowcut_ratio
C4_lowcut_sza
C4_test_cs_ref_ratio
C4_test_GLB_diff_THRES
C4_test_lowcut_ratio
C4_test_lowcut_sza
Clear_daily_ratio_lim
CLEARdir
Cloud_daily_ratio_lim
common_data_13
common_data_14
common_data_14_2
CS_file_13
CS_file_14
CS_file_14_2
csmodel
Daily_aggregation_N_lim
Daily_confidence_limit
daylist
Days_of_year
Energy_Div
fit
I1_longterm
I2_szatrend
I3_trendsconsist
ii
Input_data_ID
Kurudz_SC
lm_mean
lm_zeropoint
mean_55
mean_BR_55
mean_BR_mean
mean_BR_median
mean_BR_min
mean_mean
mean_median
mean_min
mid
MIN_ELEVA
MIN_N
mm
Monthly_aggegation_N_lim
Monthly_confidence_limit
my.cols
my.cols.gr
pyear
R_COMPILE_PKGS
RANDOM_SEED
raw_input_data
running_mean_window_days
running_mean_window_years
SEAS_MIN_N
SelEnhanc
slope_55
slope_mean
slope_median
slope_min
solar_constant
SZA_aggregation_N_lim
SZA_BIN
SZA_confidence_limit
t
tsy
units
variables_fl
xlim
yearstodo
ylim
zeropoint
zeropointA
ST_daily
ST_E_daily
ST_E_daily_seas
ST_E_monthly
ST_E_monthly_seas
ST_E_sza
ST_E_sza_doy
ST_E_sza_monthly
ST_E_yearly
ST_extreme_daily
ST_extreme_monthly
ST_extreme_SZA
ST_extreme_SZA_doy
ST_extreme_SZA_monthly
ST_extreme_total
ST_extreme_yearly
ST_G0
ST_monthly
ST_sza
ST_sza_doy
ST_sza_monthly
ST_total
ST_yearly
\end{verbatim}

@@

\begin{verbatim}
2024-08-29 10:26:26.0 athan@sagan GHI_enh_03_process.R 3.652528 mins
\end{verbatim}

>>>>

  \usepackage{unicode-math} % this also loads fontspec

@@

\ifPDFTeX\else
  % xetex/luatex font selection

@@

@@

\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}

@@

\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}

@@

\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}

@@

\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}

@@

\usepackage{bookmark}
\urlstyle{same}

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-09-05}

@@

{
\hypersetup{linkcolor=}
\setcounter{tocdepth}{4}
\tableofcontents
}
\begin{verbatim}
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
   0.00   89.58  180.00  180.00  270.42  360.00 
\end{verbatim}

\begin{verbatim}
    Min.  1st Qu.   Median     Mean  3rd Qu.     Max. 
-72.8133 -27.4706   0.7672   0.4338  28.2495  83.4876 
\end{verbatim}

@@

\subsection{Time series decomposition tests}\label{time-series-decomposition-tests}

@@

\begin{verbatim}

Call:
stats::lm(formula = .formula, data = df)

Residuals:
    Min      1Q  Median      3Q     Max 
-333.34 -132.29  -52.26   96.74  664.64

Coefficients:
                  Estimate Std. Error t value Pr(>|t|)    
(Intercept)      7.113e+00  4.604e+01   0.155    0.877    
as.numeric(Date) 2.252e-07  3.656e-08   6.160 1.98e-09 ***
---
Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Residual standard error: 189.5 on 354 degrees of freedom
Multiple R-squared:  0.09681,   Adjusted R-squared:  0.09426 
F-statistic: 37.94 on 1 and 354 DF,  p-value: 1.979e-09
\end{verbatim}

@@

\begin{verbatim}

Call:
lm(formula = ST_E_monthly$wattGLB.N ~ ST_E_monthly$Date)

Residuals:
    Min      1Q  Median      3Q     Max 
-333.34 -132.29  -52.26   96.74  664.64

Coefficients:
                   Estimate Std. Error t value Pr(>|t|)    
(Intercept)       7.113e+00  4.604e+01   0.155    0.877    
ST_E_monthly$Date 2.252e-07  3.656e-08   6.160 1.98e-09 ***
---
Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Residual standard error: 189.5 on 354 degrees of freedom
Multiple R-squared:  0.09681,   Adjusted R-squared:  0.09426 
F-statistic: 37.94 on 1 and 354 DF,  p-value: 1.979e-09
\end{verbatim}

@@

\begin{verbatim}
aa
aday
All_daily_ratio_lim
alpha
ampl
avar
BIO_ELEVA
C4_cs_ref_ratio
C4_GLB_diff_THRES
C4_lowcut_ratio
C4_lowcut_sza
C4_test_cs_ref_ratio
C4_test_GLB_diff_THRES
C4_test_lowcut_ratio
C4_test_lowcut_sza
Clear_daily_ratio_lim
CLEARdir
Cloud_daily_ratio_lim
common_data_13
common_data_14
common_data_14_2
CS_file_13
CS_file_14
CS_file_14_2
csmodel
Daily_aggregation_N_lim
Daily_confidence_limit
daylist
Days_of_year
Energy_Div
I1_longterm
I2_szatrend
I3_trendsconsist
ii
Input_data_ID
Kurudz_SC
logm_C
MIN_ELEVA
MIN_N
Monthly_aggegation_N_lim
Monthly_confidence_limit
my.cols
my.cols.gr
polyf_zero
polym_C
pyear
R_COMPILE_PKGS
RANDOM_SEED
raw_input_data
running_mean_window_days
running_mean_window_years
SEAS_MIN_N
SelEnhanc
solar_constant
SZA_aggregation_N_lim
SZA_BIN
SZA_confidence_limit
t
tsy
tzero
variables_fl
xlim
yearstodo
ylim
ST_daily
ST_E_daily
ST_E_daily_seas
ST_E_monthly
ST_E_monthly_seas
ST_E_sza
ST_E_sza_doy
ST_E_sza_monthly
ST_E_yearly
ST_extreme_daily
ST_extreme_monthly
ST_extreme_SZA
ST_extreme_SZA_doy
ST_extreme_SZA_monthly
ST_extreme_total
ST_extreme_yearly
ST_G0
ST_monthly
ST_sza
ST_sza_doy
ST_sza_monthly
ST_total
ST_yearly
\end{verbatim}

@@

\begin{verbatim}
2024-09-05 08:08:34.0 athan@sagan GHI_enh_03_process.R 5.165189 mins
\end{verbatim}

### 2024-09-05 GHI_enh_04_investigate.tex
Commit 2024-08-29 20:14
Commit 2024-08-30 20:14
Commit 2024-08-30 21:12
Commit 2024-08-31 13:12
Commit 2024-09-05 12:14

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-08-26}

@@

\begin{verbatim}
Warning: Removed 246 rows containing non-finite outside the scale range
(`stat_bin()`).
\end{verbatim}

\begin{verbatim}
Warning: Removed 27787 rows containing non-finite outside the scale range
(`stat_bin()`).
\end{verbatim}

@@

\begin{verbatim}
Warning: Removed 246 rows containing non-finite outside the scale range
(`stat_bin()`).
Removed 27787 rows containing non-finite outside the scale range
(`stat_bin()`).
\end{verbatim}

@@

\begin{verbatim}
Warning: Removed 15 rows containing non-finite outside the scale range
(`stat_bin2d()`).
\end{verbatim}

@@

lmY: 116.8672 +/- 33.89196

@@

lmY: 45.58799 +/- 10.96835

@@

lmY: 0.029427 +/- 0.054286

@@

lmY: 0.03518 +/- 0.042507

@@

lmY: 116.3147 +/- 30.85223

@@

lmY: 45.55073 +/- 10.16657

@@

\caption{ - empty caption - }\label{fig:P-MW-energy-2}
\end{figure}
\begin{figure}[H]

@@

\begin{verbatim}
2024-08-26 19:52:09.6 athan@sagan GHI_enh_04_investigate.R 0.838254 mins
\end{verbatim}

>>>>

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-09-05}

@@

\begin{verbatim}
Warning: Removed 220 rows containing non-finite outside the scale range
(`stat_bin()`).
\end{verbatim}

\begin{verbatim}
Warning: Removed 26591 rows containing non-finite outside the scale range
(`stat_bin()`).
\end{verbatim}

@@

\begin{verbatim}
Warning: Removed 220 rows containing non-finite outside the scale range (`stat_bin()`).
Removed 26591 rows containing non-finite outside the scale range (`stat_bin()`).
\end{verbatim}

@@

\begin{verbatim}
Warning: Removed 14 rows containing non-finite outside the scale range
(`stat_bin2d()`).
\end{verbatim}

@@

lmY: 226.3963 +/- 31.30176

@@

lmY: 85.26719 +/- 10.01748

@@

lmY: 0.116043 +/- 0.055572

@@

lmY: 0.107931 +/- 0.044598

@@

lmY: 222.2785 +/- 28.96957

@@

lmY: 83.81382 +/- 9.456821

@@

\caption{ - empty caption - }\label{fig:P-MW-energy-2}
\end{figure}

\hypertarget{yearly-trends-with-data-completeness}{%
\subsection{Yearly trends with data completeness}\label{yearly-trends-with-data-completeness}}

lmY: 229.8063 +/- 39.56838

{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/P-energy-complete-1}

\caption{ - empty caption - }\label{fig:P-energy-complete-1}
\end{figure}

lmY: 86.21667 +/- 12.87325

{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/P-energy-complete-2}

\caption{ - empty caption - }\label{fig:P-energy-complete-2}
\end{figure}

lmY: 0.085425 +/- 0.09766

{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/P-energy-complete-3}

\caption{ - empty caption - }\label{fig:P-energy-complete-3}
\end{figure}

lmY: 0.086495 +/- 0.070955

{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/P-energy-complete-4}

\caption{ - empty caption - }\label{fig:P-energy-complete-4}
\end{figure}
\begin{figure}[H]

@@

\begin{verbatim}
2024-09-05 08:56:04.2 athan@sagan GHI_enh_04_investigate.R 13.014418 mins
\end{verbatim}
